# Covid Assignment

Import libraries
```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(rmarkdown)
```

Import data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Dropbox/code/r/iData/assignment-covid/git-repo")
getwd()
```

```{r}
data <- read.csv("data.csv")
```

## Variable Information

Sampling Variables

| Variable | Description                             |
|:--------:|:---------------------------------------:|
| ID       | Respondant id number                    |
| DATE     | Interview Date                          |
| Q1       | Governorate                             |
| WT       | Weight for the probability of selection | 


| Code | Country |
|:----:|:-------:|
| 1    | ALGERIA |
| 7    | IRAQ    |
| 8    | JORDAN  |
| 9    | KUWAIT  |
| 10   | LEBANON |
| 11   | LIBYA   |
| 13   | MOROCCO |
| 21   | TUNISIA |


Create a tidy dataset for Iraq, relocate the WT column to before the questions
begin.

```{r}
dataRow <- data |>
  filter(COUNTRY == 7) |>
  select(-COUNTRY) |>
  relocate(WT, .before = Q1)
```

The pivot_longer() creates tidy data.

```{r}
dataRow <- dataRow |>
  pivot_longer(cols = 5:105, names_to = "Question",
               values_to = "Answers") |>
  mutate(DATE = ymd(DATE))
```

```{r}
head(dataRow)
```

Summary stats of Age
```{r}
dataRow |>
  filter(Question == "Q1001") |>
  summary(Answers)
```

The youngest participant was 18 years old, the oldest was 70 years old, the mean
(average) was around 35 years old while the median was 33.

```{r}
dataRow |>
  filter(Question == "Q1002") |>
  count(Answers)
```
There are 515 females and 501 males.

## Visualizations

Quick bar graph of any question.
```{r}
questionNumber = "Q609"
iraq_tidy_bar_graph <- 
  dataRow |>
    filter(Question == questionNumber & Answers < 10)

ggplot(iraq_tidy_bar_graph, aes(x = Answers)) +
#  geom_bar(fill = "white", colour = "black", width = 0.50) +
  geom_histogram(fill = "white", colour = "black", bins = 3) +
  theme_bw()
```
## Governmate Analysis
Trust in the Government and Courts

Trust in the Armed forces and Religious leaders

## Age vs Religion

```{r}
age_religiousness <- iraq |>
  select(Q609, Q1001) |>
  filter(Q1001 <= 24 & Q1001 >= 18 & Q609 < 10)

age_religiousness_2 <- iraq |>
  select(Q609, Q1001) |>
  filter(Q1001 <= 31 & Q1001 >= 25 & Q609 < 10)

ggplot(age_religiousness, aes(x = Q609)) +
  geom_bar(fill = "white", colour = "black")

ggplot(age_religiousness_2, aes(x = Q609)) +
  geom_bar(fill = "white", colour = "black")
```



## Breaks attempt #1

```{r}
iraq$groups <- cut(iraq$Q1001, breaks = c(17,24,30,36,42,48,54,60,66,72,Inf))

table(cut(iraq$Q1001, breaks=c(17,24,30,36,42,48,54,60,66,72,Inf)))

table(cut(iraq$Q609, breaks=c(1,2,3,Inf)))
```

## Breaks attempt #2
```{r}
data_values_range <- iraq |>               # Aggregate values in range
  mutate(ranges = cut(Q609,
                      c(1,2,3.4))) |> 
  group_by(ranges) |>
  dplyr::summarize(sums = sum(Q609)) |>
  as.data.frame()
data_values_range                                  # Print aggregated values in range
```

## Change column names
The team agreed to use a camel case for the column names.
```{r}
dataColumns <- data |>
  ## Rename sampling variables
  rename(x = X,
         country = COUNTRY,
         id = ID,
         data = DATE,
         govornorate = Q1,
         citySize = Q13A,
         probabilityOfSelection = WT) |>
  ## Rename demogrpahics
  rename(age    = Q1001,
         gender = Q1002) |>
  ## Rename Section III questions.
  rename(currentEconomicSituation                    = Q101,
         futureEconomicSituation                     = Q102,
         statementWorriedFoodRunOut                  = Q112_1,
         statementFoodDidNotLastAndWeDidNotHaveMoney = Q112_2,
         importantIssueToFocusOn                     = Q118) |>
  ## Rename Section V question.
  rename(trustInGov                      = Q201A_1,
         trustInCourt                    = Q201A_2,
         trustInArmy                     = Q201B_6,
         trustInReligiousLeaders         = Q201B_13,
         satisfactionWithGovPerformance  = Q204A_1,
         satisfactionWithEducationSystem = Q204A_2,
         satisfactionWithHealthcare      = Q204A_3,
         guarnteeOfFreedomOfOpinions     = Q521_1 ,
         guarnteeOfFreedomOfMedia        = Q521_2 ,
         guarnteeOfFreedomOfPortest      = Q521_4 ,
         performanceOnSecurity           = Q204_11,
         performanceOnLowPrices          = Q204_20,
         performanceOnCovidResponse      = Q204_25,
         corruptionInAgencies            = Q210   ,
         workAgainstCorruption           = Q211  ) |>
  ## Rename demographics columns
  rename(levelOfEducation     = Q1003,
         socialStatus         = Q1010,
         children             = Q1010B1,
         childrenInSchool     = Q1010B2,
         householdPeople      = Q1014C,
         workStatus           = Q1005,
         pension              = Q1005B,
         lookingForJob        = Q1005C,
         whyNotLookingForJob  = Q1005D,
         householdWork        = Q1005E,
         workSector           = Q1006A,
         industryDescription  = Q1006B_CODE,
         netHouseholdIncome   = Q1016,
         religion             = Q1012,
         religionDenomination = Q1012A,
         ethnicity            = Q1012B,
         religiousOrNot       = Q609)

# | [a-z]*\ *|\ q[0-9]*_?[0-9]*\ *|
```

Drop the columns whose name starts with Q
```{r}
dataColumns <- dataColumns[, -grep("Q[0-9]*", colnames(dataColumns))]

colnames(dataColumns)

dataColumns <- 
  dataColumns |> 
  filter(country == 7)
```

## Cultivar data frame for stacked bar graph
Culitvar is the answer variable, the other variable is the age.

```{r}
# stacked_bar_graph <-
variable_two = "religiousOrNot"


data_clean_bar <-
  dataColumns |>
  select(age, variable_two) |>
  filter(religiousOrNot < 4) |>
  filter(age < 90) 

ggplot(data_clean_bar, aes(x = age, y = religiousOrNot, fill = religiousOrNot)) +
  geom_col()
  
stacked_bar_graph <-
  dataColumns |>
  select(age, religiousOrNot) |>
  filter(religiousOrNot < 4) |>
  filter(age < 90) |>
  group_by(religiousOrNot, age) |>
  count()

colnames(stacked_bar_graph)
# "religiousOrNot" "age"  "n"             

ggplot(stacked_bar_graph, aes(x = age, y = n, fill = religiousOrNot)) +
  geom_col()
```

## Age investigation
```{r}
data_clean_age_counts <- data_clean |>
  select(age) |>
  filter(age < 100) |>
  group_by(age) |>
  count()

data_clean_age_counts[order(data_clean_age_counts$n, decreasing = T), ]

data_clean_ages <-
  data_clean |>
  select(age) |>
  filter(age < 90)
  
ggplot(data_clean_ages, aes(x = age)) +
  geom_bar(fill = "white", colour = "black", width = 0.50) +
#  geom_histogram(fill = "white", colour = "black", bins = 3) +
  theme_bw()    
```
