# Covid Assignment

Import libraries
```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(rmarkdown)
```

Import data
```{r}
setwd("~/Dropbox/code/r/iData/assignment-covid/git-repo")
data <- read.csv("data.csv")
```

## Variable Information

Sampling Variables

| Variable | Description                             |
|:--------:|:---------------------------------------:|
| ID       | Respondant id number                    |
| DATE     | Interview Date                          |
| Q1       | Governorate                             |
| WT       | Weight for the probability of selection | 


| Code | Country |
|:----:|:-------:|
| 1    | ALGERIA |
| 7    | IRAQ    |
| 8    | JORDAN  |
| 9    | KUWAIT  |
| 10   | LEBANON |
| 11   | LIBYA   |
| 13   | MOROCCO |
| 21   | TUNISIA |


Create a tidy dataset for Iraq, relocate the WT column to before the questions
begin.

```{r}
iraq <- data |>
  filter(COUNTRY == 7) |>
  select(-COUNTRY) |>
  relocate(WT, .before = Q1)
```

The pivot_longer() creates tidy data.

```{r}
iraq_tidy <- iraq |>
  pivot_longer(cols = 5:105, names_to = "Question",
               values_to = "Answers") |>
  mutate(DATE = ymd(DATE))
```

Summary stats of Age
```{r}
iraq_tidy |>
  filter(Question == "Q1001") |>
  summary()
```

The youngest participant was 18 years old, the oldest was 70 years old, the mean
(average) was around 35 years old while the median was 33.

```{r}
iraq_tidy |>
  filter(Question == "Q1002") |>
  count(Answers)
```
There are 515 females and 501 males.

## Visualizations

Quick bar graph of any question.
```{r}
questionNumber = "Q1005D"
iraq_tidy_bar_graph <- 
  iraq_tidy |>
    filter(Question == questionNumber & Answers < 10)

ggplot(iraq_tidy_bar_graph, aes(x = Answers)) +
  geom_bar(fill = "white", colour = "black", width = 0.50) +
  theme_bw()
```
## Governmate Analysis
Trust in the Government and Courts

Trust in the Armed forces and Religious leaders
